%% start of file `template.tex'.
%% Copyright 2006-2010 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.

\documentclass[11pt, a4paper, nolmodern]{moderncv}

\usepackage{GuillaumePapin}

\usepackage[english]{babel}

%% \title{CS Student \& teaching assistant} % optional, remove the line if not wanted

%% Personal data
\mobile{(+33) 614 534 392}   % optional, remove the line if not wanted
%% \extrainfo{20 years}         % optional, remove the line if not wanted
\address{13, rue du Bois Guillet}{44450 Barbechat\\
France}                      % optional, remove the line if not wanted

\newcommand \objectives {To acquire new skills in object-oriented
  programming, artificial intelligence and software design. Also
  interested in learning new methodologies and sharing knowledge in a
  team.}

%% \quote{\textbf{Objective:} ``\objectives''} % optional, remove the line if not wanted

%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
\maketitle

\section{Objective}
\cvline{}{\objectives}

\section{Education}
% arguments 3 to 6 can be left empty
%% \cventry{years}{degree/job title}{institution/employer}
%% {opt: localization}{opt: grade/...}{opt: comment/job description}
%% \tllabelcventry{2009}{2012}{2009--Today}
%% \tlsince{Since }
\tlcventry{2009}{0}
               {\nth{3} year student}{\Colorhref[dark-grey]{http://www.epitech.eu/}{EPITECH}}{Nantes}{France}
               {\begin{itemize}
\item Multiple experiences in designing and coding cross-platform
  client/server applications using C++ and C.
\item Excellent ability to work in a team environment and good skills
  in project management.
\end{itemize}}
\tlcventry{2006}{2009}{Baccalauréat, \small equivalent of British A Level}
          {\Colorhref[dark-grey]{http://www.la-joliverie.com/}{la Joliverie}}
          {France}{}
          {Industrial Sciences and Technologies - \textit{Mechanical and Production Engineering}}

\section{Experience}
\tlcventry{2011}{0}{Teaching
  assistant}{\Colorhref[dark-grey]{http://www.epitech.eu/}{EPITECH}}{Nantes}{France}
          {Provide technical support for \nth{1} and \nth{2} years
            students in C and C++ programming language on Linux.
\begin{itemize}
\item Responsible for their evaluations.
\item Good communication skills.
\end{itemize}}
\tllabelcventry{2010}{2011}{2010}
               {Analysis, design and development in Java}
               {\Colorhref[dark-grey]{http://www.groupe-sii.com/en/home}{SII Group}}
               {Nantes}{France \textit{(6 month internship)}}
               {Developing a requirements extraction tool.
\begin{itemize}
\item Experience all phases of the software development life cycle:
  requirements specification, design, implementation, documentation,
  unit testing, acceptance testing and software release.
\item \textit{Partial} application of the {\Colorhref[dark-grey]{http://www.sei.cmu.edu/cmmi/}{CMMI}} standard.
\end{itemize}}

\section{Computer Knowledge \& Skills}
\cvcomputer{\textbf{Proficient}}{C++, C, Java, Bash, Elisp, JSON, XML}
           {\textbf{Some experiences}}{Ruby, Lua, MySQL, Perl, ASM (x86), J2EE}
\cvcomputer{\textbf{IDE}}{Emacs, Visual Studio, Eclipse, QtCreator}
           {\textbf{Tools}}{GCC, Clang, Make, CMake, GDB, Valgrind, Doxygen}
\cvcomputer{\textbf{Operating systems}}{GNU/Linux, Windows XP/7, BSD}
           {\textbf{SCM}}{Git, Mercurial, Subversion}
\cvcomputer{\textbf{Continuous integration}}{Jenkins, Hudson}
           {\textbf{Project management}}{Redmine, Bugzilla/Testopia, Github}
%% \cvcomputer{\textbf{Project tools}}{Jenkins, Hudson, Redmine, Bugzilla with Testopia, Github}
%%            {\textbf{Methodology}}{UML, Unit testing, Design patterns, \ldots}

\section{Foreign Languages}
%% \cvlanguage{English}{Fluent \textit{(Technical)}}{}
\cvline{\textbf{English}}{Fluent \textit{(Technical)}}

\section{Hobbies \& Interests}
\cvhobby{Programming}{Github profile: \Colorhref[dark-grey]{https://github.com/Sarcasm}{github.com/Sarcasm}}
\cvhobby{Sport}{Running \textit{(member of an association - \Colorhref[dark-grey]{http://run-away.fr}{run-away.fr)}}}
\end{document}
